% !TeX root = RL_main.tex

\documentclass[a4paper,twocolumn]{article}
%\documentclass{article}

\input{./RL_src/RL_0_packages}
\input{./RL_src/RL_0_defs}





\def\thesubsubsection{\arabic{subsubsection}}
\titleformat{\subsubsection}[runin]
{\normalfont\bfseries}
{\indent\thesubsubsection)}{0.5em}{}
\title{Reply Letter for GRSL-00116-2025}

\author{%
	Yudai Inada, Shingo Takemoto, Shunsuke Ono\\
	Institute of Science Tokyo\\
	inada.y.de71@m.isct.ac.jp, takemoto.s.e908@m.isct.ac.jp, ono.s.5af2@m.isct.ac.jp\\
}


\begin{document}
\onecolumn
\maketitle
\begin{flushleft}
	Paper Number: GRSL-00116-2025\\
	Title: Efficient and Accurate Full-Waveform Inversion with Total Variation Constraint\\
	Date of Evaluation: 14-Jan-2025.\\
	Date for Revision: 28-May-2024.\\
\end{flushleft}

We would like to take this opportunity to thank Dr. Xiuping Jia
for kindly handling our manuscript and the reviewers for their carefully reading of our manuscript and giving useful comments.
Furthermore, we also appreciate the recommendation to resubmit to the Journal of Selected Topics in Applied Earth Observations and Remote Sensing.
We have carefully studied all the comments given by the associate editor and the reviewers and have made revisions,
which we hope will meet with your approval.
Please kindly see the following pages that contain our detailed responses to each comment raised by the associate editor and each reviewer.
We have also uploaded a PDF file of the revised manuscript,
where we changed the text color to blue in revised parts.

All numberings (of sections, equations, references, etc.) in the original comments given by the reviewers refer to the previous manuscript, and those in the following replies refer to the revised manuscript. We have highlighted significant changes in the revised manuscript and the replies in \textcolor{blue}{blue}.
% The numberings of sections and equations in the following answers refer to the revised manuscript,
% and all the references in the following answers are given at the end of the letter.

We are grateful for your help and comments, which enabled us to significantly improve the quality of our paper.
We hope that our response is sufficient to make our manuscript suitable for publication in the IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing.

\twocolumn
\clearpage
%	\section*{Notes on revision made to manuscript Paper $\#$ABC-2099-12-1234
%	}
%	\vspace{10pt}
%	
%	The authors would like to thank the editor and reviewers for their constructive comments and suggestions that have helped improve the quality of this manuscript. The manuscript has undergone a thorough revision according to the editor and reviewers’ comments. Please see below our responses. For the reviewers’ convenience, we have highlighted significant changes in the revised manuscript in \textcolor{blue}{blue}.
	
% Let's start point-by-point with Reviewer 1

\onecolumn
\section*{Response to the Associate Editor}
% General intro text goes here
\begin{point1}
(There are no comments.)
\end{point1}


\begin{reply}
Thank you very much for handling our paper carefully. Following the instruction, we have provided an item-by-item response to the reviewer's comments. Although the details are described in the answers to each reviewer's comment, we would like to summarize the main revisions in brief:

\begin{itemize} 
	\item We have reorganized the paragraphs in the Introduction for improved readability. (For the reply to Comment 1.1)
	\item We have improved the description of the proposed method. (For the replies to Comments 1.5, 2.1, 2.3, and 3.1)
	\item We have added references and comparative methods. (For the replies to Comments 1.2, 1.3, 1.4, 2.6, 3.2, and 3.5)
	\item We have conducted additional experiments with additional noise conditions. (For the replies to Comments 1.4, 2.5, and 3.4)
	\item We have expanded the experiments by incorporating an additional dataset. (For the reply to Comment 1.5)
	\item We have conducted further analysis of the proposed method. (For the replies to Comments 2.3 and 2.7)
\end{itemize}

%\begin{itemize}
%	\item We have added additional references. (For the replies to Comment 2.1, 2.2, and 3.1)
%	\item We have rewritten the contributions to be clearer. (For the replies to Comment 1.1, 1.2, 1.3, 1.4, 3.2, and 3.3)
%	\item We have improved the description of our method. (For the replies to Comment 1.1, 3.2, and 3.3)
%	\item We have performed substantial additional experiments. (For the replies to Comment 2.4, 2.5, 3.4, 3.5, 3.6, 3.7)
%\end{itemize}
\end{reply}


\twocolumn
\clearpage

\twocolumn[
\section*{Response to Reviewers}
]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection
% General intro text goes here

\input{./RL_src/RL_1_0_Gen}

\setcounter{point}{0}

%%%%%%%%%%%%%%%%
\input{./RL_src/RL_1_1}
\input{./RL_src/RL_1_2}
\input{./RL_src/RL_1_3}
\input{./RL_src/RL_1_4}

%\input{./RL_src/RL_1_Appendix}
\input{./RL_src/RL_1_bib}
%%%%%%%%%%%%%%%%





\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection


\input{./RL_src/RL_2_0_Gen}

\setcounter{point}{0}

%%%%%%%%%%%%%%%%
\input{./RL_src/RL_2_1}
\input{./RL_src/RL_2_2}
\input{./RL_src/RL_2_3}
\input{./RL_src/RL_2_4}
\input{./RL_src/RL_2_5}
\input{./RL_src/RL_2_6}
\input{./RL_src/RL_2_7}
\input{./RL_src/RL_2_8}

%\input{./RL_src/RL_2_Appendix}
\input{./RL_src/RL_2_bib}

%%%%%%%%%%%%%%%%



\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection


\input{./RL_src/RL_3_0_Gen}

\setcounter{point}{0}

%%%%%%%%%%%%%%%%
\input{./RL_src/RL_3_1}
\input{./RL_src/RL_3_2}
\input{./RL_src/RL_3_3}
\input{./RL_src/RL_3_4}
\input{./RL_src/RL_3_5}
\input{./RL_src/RL_3_6}
\input{./RL_src/RL_3_7}
\input{./RL_src/RL_3_8}
\input{./RL_src/RL_3_9}

%\input{./RL_src/RL_3_Appendix}
%\input{./RL_src/RL_3_bib}

%%%%%%%%%%%%%%%%







\end{document}


