\begin{thebibliography}{100}
	\bibitem[16]{Zhuang2023FastHyMix} L. Zhuang and M. K. Ng, ``FastHyMix: Fast and paramter-free hyperspectral image mixed noise removal,'' \textit{IEEE Trans. Neural Netw. Learn. Syst.,} vol. 34, no. 8, pp. 4702-4716, 2023.
	
%	\bibitem[17]{Peng2024RCILD} J. Peng, H. Wang, X. Cao, Q. Zhao, J. Yao, H. Zhang, and D. Meng, ``Learnable Representative Coefficient Image Denoiser for Hyperspectral Image,'' \textit{IEEE Trans. Geosci. Remote Sens.}, vol. 62, pp. 1-16, 2024.
	
	\bibitem[25]{Aggarwal2016SSTV} H. K. Aggarwal and A. Majumdar, ``Hyperspectral Image Denoising Using Spatio-Spectral Total Variation,'' \textit{IEEE Geosci. Remote Sens. Lett.}, vol.13, no. 3, pp. 442-446, 2016.
	
	\bibitem[28]{Takeyama2020HSSTV} S. Takeyama, S. Ono, and I. Kumazawa, ``A Constrained Convex Optimization Approach to Hyperspectral Image Restoration with Hybrid Spatio-Spectral Regularization,'' \textit{Remote Sens.}, vol. 12, no. 21, 2020.
	
	\bibitem[29]{Wang2021l0l1HTV} M. Wang, Q. Wang, J. Chanussot, and D. Hong, ``$l_0$-$l_1$ Hybrid Total Variation Regularization and its Applications on Hyperspectral Image Mixed Noise Removal and Compressed Sensing,'' \textit{IEEE Trans. Geosci. Remote Sens.}, vol. 59, no. 9, pp. 7695-7710, 2021. 
	
	\bibitem[34]{Wang2018LRTDTV} Y. Wang, J. Peng, Q. Zhao, Y. Leung, X. Zhao, and D. Meng, ``Hyperspectral Image Restoration Via Total Variation Regularized Low-Rank Tensor Decomposition,'' \textit{IEEE J. Sel. Topics Appl. Earth Observ. Remote Sens.}, vol. 11, no. 4, pp. 1227-1243, 2018.
	
%	\bibitem[35]{Chen2020LRTDGS} Y. Chen , W. He, N. Yokoya, and T.-Z. Huang, ``Hyperspectral Image Restoration Using Weighted Group Sparsity-Regularized Low-Rank Tensor Decomposition,'' \textit{IEEE Trans. Cybern.}, vol. 50, no. 8, pp. 3556-3570 2020.
	
	\bibitem[36]{Chen2022FGSLR} Y. Chen, T. Huang, W. He, X. Zhao, H. Zhang, and J. Zeng, ``Hyperspectral Image Denoising Using Factor Group Sparsity-Regularized Nonconvex Low-Rank Approximation,'' \textit{IEEE Trans. Geosci. Remote Sens.}, vol. 60, pp. 1-16, 2022.
	
	\bibitem[37]{Chen2023TPTV} Y. Chen, W. Cao, L. Pang, J. Peng, and X. Cao, ``Hyperspectral Image Denoising Via Texture-Preserved Total Variation Regularizer,'' \textit{IEEE Trans. Geosci. Remote Sens.}, vol. 61, pp. 1-14, 2023.	
	
	\bibitem[38]{Lefkimmiatis2015STV} S. Lefkimmiatis, A. Roussos, P. Maragos, and M. Unser, ``Structure Tensor Total Variation,'' \textit{SIAM J. Imag. Sci.}, vol. 8, no. 2, pp. 1090--1122, 2015. 
	
	\bibitem[41]{Kurihara2017SSST} R. Kurihara, S. Ono, K. Shirai, and M. Okuda, ``Hyperspectral image restoration based on spatio-spectral structure tensor regularization,'' \textit{Proc. Eur. Signal Process. Conf. (EUSIPCO)}, pp. 488-492, 2017.
	
%	\bibitem[42]{Forstner1987Fast} W. F{\"o}rstner and E. G{\"u}lch, ``A fast operator for detection and precise location of distinct points, corners and centres of circular features,'' \textit{Proc. ISPRS Intercommission Conf. Fast Process. Photogramm. Data}, vol. 6, pp. 281--305, 1987.
	
%	\bibitem[43]{Weickert1998Anisotropic} J. Weickert, ``Anisotropic diffusion in image processing,'' \textit{Stuttgart, Germany: B. G. Teubner}, vol. 1, 1998.
	
%	\bibitem[44]{Jahne2005Digital} B. J{\"a}hne, ``Digital image processing,'' \textit{Springer Sci. Bus. Media}, 2005.
	
	\bibitem[52]{Pock2011PPDS} T. Pock and A. Chambolle, ``Diagonal preconditioning for first order primal-dual algorithms in convex optimization,'' \textit{Proc. IEEE Int. Conf. Comput. Vis. (ICCV)}, pp. 1762--1769, 2011.
	
	\bibitem[60]{Wang2004SSIM} Z. Wang, A. Bovik, H. Sheikh, and E. Simoncelli, ``Image quality assessment: from error visibility to structural similarity,'' \textit{IEEE Trans. Image Process.}, vol. 13, no. 4, pp. 600-612, 2004.
	
	
	\bibitem[61]{Matsaglia1974Equalities} G. Matsaglia and G. PH Styan, ``Equalities and inequalities for ranks of matrices,'' \textit{Linear multilinear Algebra}, vol. 2, no. 3, pp. 269--292, 1974.
	
	
\end{thebibliography}